---
title: "v2 Code for random slope model"
author: "Fonti Kar"
date: "12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
sessionInfo()
#R version 3.4.2 (2017-09-28)
#Platform: x86_64-apple-darwin15.6.0 (64-bit)
#Running under: macOS High Sierra 10.13.6

packages.need <- c("ggplot2", "tidyverse", "dplyr", "magrittr", "MCMCglmm", "brms", "RColorBrewer", "latex2exp")

lapply(packages.need, require, character.only = TRUE)


source("R/functions/unpacking.R")
source("R/functions/smr_functions.R")
```

The code below is uses a function-valued approach in the MCMCglmm package to calculate: 
a) repeatability of the reaction norm slope (sensu Araya-Ajoy et al 2015) 

## Read in long format data first and load helper functions

```{r load data}
data <- read.csv("data/data_final/Long_data_ldeli_metabR.csv")
str(data)
dim(data)

source("R/functions/unpacking.R")
source("R/functions/smr_functions.R")
```

##Complete data in predictors are needed

```{r}
complete_data <- data %>% filter(complete.cases(incb_temp) & complete.cases(z.log.mass) & complete.cases(prior_temp))
str(complete_data)
dim(complete_data)
```
###Expanded paramater prior for model and model set up 

```{r}
expanded.prior <- list(G = list(G1 = list(V = diag(2), nu = 0.002, alpha.V = diag(1000,2,2), alpha.mu = rep(0,2)),
                                G2 = list(V = diag(2), nu = 0.002, alpha.V = diag(1000,2,2), alpha.mu = rep(0,2)),
                                G3 = list(V = 1, nu = 0.002, alpha.V = 1000, alpha.mu = 0)),
                       R = list(V = 1, nu = 0.002))


#Number of iterations, burn in and thinning interval
nitt = 7510000
burnin = 10000
thin = 5000
```

## The model

```{r}
mod1.2.1 <- mclapply(1:3, function(i) {
  MCMCglmm(log.co2pmin ~ incb_temp + z.log.mass + prior_temp,
           random = ~us(1+incb_temp):id + us(1+incb_temp):id:samp_period + id:samp_period:incb_temp,
           rcov = ~id:samp_period:incb_temp:rep_id
           family = "gaussian",
           prior = expanded.prior,
           nitt = nitt,
           burnin = burnin,
           thin = thin,
           data = complete_data, 
           verbose = T)
}, mc.cores = 3)

mod1.2.2 <- mclapply(1:3, function(i) {
  MCMCglmm(log.co2pmin ~ incb_temp + z.log.mass + prior_temp,
           random = ~us(1+incb_temp):id + us(1+incb_temp):series + id:samp_period:incb_temp,
           family = "gaussian",
           prior = expanded.prior,
           nitt = nitt,
           burnin = burnin,
           thin = thin,
           data = complete_data, 
           pr = T,
           verbose = T)
}, mc.cores = 3)

mod1.2.4 <- mclapply(1:3, function(i) {
  MCMCglmm(log.co2pmin ~ incb_temp + z.log.mass + prior_temp,
           random = ~us(1+incb_temp):id + us(1+incb_temp):series,
           rcov = ~id:samp_period:incb_temp:rep_id,
           family = "gaussian",
           prior = expanded.prior,
           nitt = nitt,
           burnin = burnin,
           thin = thin,
           data = complete_data,
           pr = T,
           verbose = T)
}, mc.cores = 3)
```

## Unpack
## mod1.2.1

```{r}
#Read in model output and pool chains
mod1.2.1 <- readRDS("R/Revision/output/rds/mod1.2.1")
mod1.2.1.Sol <- Sol.unpack("R/Revision/output/rds/mod1.2.1")
mod1.2.1.VCV <- VCV.unpack("R/Revision/output/rds/mod1.2.1")

#Diagnostics
#Sol.check("R/Revision/output/rds/mod1.2.1")
#VCV.check("R/Revision/output/rds/mod1.2.1")

#Summary of model output
summary(mod1.2.1[[1]])
str(mod1.2.1[[1]])
posterior.mode(mod1.2.1[[1]]$VCV)

#Calculating the repeatability of slope and credible intervals
rpt.Slope.mean(mod1.2.1.VCV, "incb_temp:incb_temp.id", "incb_temp:incb_temp.series")
rpt.Slope.mode(mod1.2.1.VCV, "incb_temp:incb_temp.id", "incb_temp:incb_temp.series")
```

# #Error in readRDS("R/Revision/output/rds/mod1.2.2") : 
#   ReadItem: unknown type 192, perhaps written by later version of R
```{r}
#Read in model output and pool chains
mod1.2.2 <- readRDS("R/Revision/output/rds/mod1.2.4")

# #Error in readRDS("R/Revision/output/rds/mod1.2.2") : 
#   ReadItem: unknown type 192, perhaps written by later version of R

mod1.2.2.Sol <- Sol.unpack("R/Revision/output/rds/mod1.2.2")
mod1.2.2.VCV <- VCV.unpack("R/Revision/output/rds/mod1.2.2")

#Diagnostics
Sol.check("R/Revision/output/rds/mod1.2.2")
VCV.check("R/Revision/output/rds/mod1.2.2")

#Calculating the repeatability of slope and credible intervals
rpt.Slope.mean(mod1.2.2.VCV, "log.temp:log.temp.id", "log.temp:log.temp.series")
```

## mod1.2.4

```{r}
#Read in model output and pool chains
mod1.2.4 <- readRDS("R/Revision/output/rds/mod1.2.4_noidsampertemp")
mod1.2.4.Sol <- Sol.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")
mod1.2.4.VCV <- VCV.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")

#Diagnostics
Sol.check("R/Revision/output/rds/mod1.2.4_noidsampertemp")
VCV.check("R/Revision/output/rds/mod1.2.4_noidsampertemp")

#Summary of model output
summary(mod1.2.4[[1]])
str(mod1.2.4[[1]])
posterior.mode(mod1.2.4[[1]]$VCV)
colnames(mod1.2.4[[1]]$VCV)
colnames(mod1.2.4[[1]]$Sol)

#Calculating the repeatability of slope and credible intervals
rpt.Slope.mean(mod1.2.4.VCV, "incb_temp:incb_temp.id", "incb_temp:incb_temp.series")
rpt.Slope.mode(mod1.2.4.VCV, "incb_temp:incb_temp.id", "incb_temp:incb_temp.series")
```


### Model estimating BLUPS for each individual. This model is use for generating model predicted reaction norms

```{r}
mod1.2.3 <- mclapply(1:3, function(i) {
  MCMCglmm(log.co2pmin ~ incb_temp + z.log.mass + prior_temp,
           random = ~us(1+incb_temp):id + us(1+incb_temp):series + id:samp_period:incb_temp,
           family = "gaussian",
           prior = expanded.prior,
           nitt = nitt,
           burnin = burnin,
           thin = thin,
           data = complete_data, 
           pr = T,
           verbose = T)
}, mc.cores = 3)


# saveRDS(mod1.2.3 , "R/mod1.2.3")

#Read in model output and pool chains
mod1.2.3 <- readRDS("R/Revision/output/rds/mod1.2.3")
mod1.2.3.Sol <- Sol.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")
mod1.2.3.VCV <- VCV.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")

#Diagnostics
Sol.check("R/Revision/output/rds/mod1.2.4_noidsampertemp")
VCV.check("R/Revision/output/rds/mod1.2.4_noidsampertemp")

```

#Theme for all ggplots

```{r}
my_theme <- theme_bw() + 
  theme(legend.position = "none", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=14),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18)) 
```
        
```{r}
#Fig 3A Reaction norms character state approach
mod1.2.3.Sol <- Sol.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")
mod1.2.3.VCV <- VCV.unpack("R/Revision/output/rds/mod1.2.4_noidsampertemp")

# Here are the six incubator temperatures, 
temps <- unique(data$incb_temp)

#and the 42 lizard names
ids <- data$id %>% as.character %>% unique %>% sort
ids_2 <- ids[-9]

output <- do.call("rbind", lapply(c(1,5,10), function(i){
do.call("rbind", lapply(ids_2, get.predictions, post=cbind(mod1.2.3.Sol, mod1.2.3.VCV), sampling.period = i)) %>% 
    mutate(sampling.period = i) %>%
    arrange(Temperature, predicted) %>% 
    mutate(Lizard = factor(Lizard, levels = unique(Lizard)))
}))

saveRDS(output, "R/RMDs/output/mod1.2.3.predictions.csv")
output <- readRDS("R/RMDs/output/mod1.2.3.predictions.csv")

#Plotting reaction norms for sample period 1,5,10
reaction.norms <- output %>% group_by(Temperature, Lizard, sampling.period) %>% 
  summarise(posterior.mean = mean(as.mcmc(predicted)), 
            lower = as.numeric(HPDinterval(as.mcmc(predicted)))[1], 
            upper = as.numeric(HPDinterval(as.mcmc(predicted)))[2])

#Plot of reaction norms at sampling period 1, 5, 10 and show slopes are repeatable over time
#pdf("output/fig/pT/repeatability_of_slope.pdf", 12,9)
n <- length(ids_2)
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))

set.seed(10)
my_cols <- sample(col_vector, n, replace = F) ; pie(rep(1,n), col=my_cols)

#Sample 10 random lizards
set.seed(10)
subset_ids <- sample(ids_2, 10)

reaction.norms %>% filter(Lizard %in% subset_ids) %>% 
  ggplot(aes(x = Temperature, y = posterior.mean, color = Lizard)) + 
  geom_point(shape = 1, fill = "white", size = 1, color = "black") + 
  geom_line(aes(group = Lizard, colour = Lizard), stat="smooth", method = "lm", alpha = 0.7) +
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  scale_color_manual(values = my_cols) +
  facet_wrap(~ sampling.period) + 
  labs(x = expression(paste("Temperature ",degree,"C")), y = TeX("log VCO_2 mL min^{-1}")) + 
    my_theme
```


