---
title: "v2 Code for multivariate response model"
author: "Fonti Kar"
date: "12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, include = T)
rm(list=ls())
sessionInfo()
#R version 3.4.2 (2017-09-28)
#Platform: x86_64-apple-darwin15.6.0 (64-bit)
#Running under: macOS High Sierra 10.13.6

packages.need <- c("ggplot2", "tidyverse", "magrittr", "brms", "corrplot", "patchwork")
lapply(packages.need, require, character.only = TRUE)
```

The code below is uses a character-state approach in the brms package to estimate: 
a) adjusted repeatability (sensu Nakagawa & Schielzeth, 2010) of VCO2 at each measurement temperature 
b) among- and within-individual variance components at each measurement temperature
c) cross-temperature correlations (sensu Brommer 2013) of VCO2 between each measurement temperature at the among- and within-individual level

## Read in wide format data first and source helper functions

```{r load data}
wdata <- read.csv("data/data_final/Wide_data_ldeli_metabR.csv")
ldata <- read.csv("data/data_final/Long_data_ldeli_metabR.csv")

str(data)
dim(wdata)

source("R/functions/unpacking.R")
source("R/RMDs/helper_functions.R")
```

## Model set up 

```{r}
#Model set up
iter = 5000
warmup = iter/2
thin = 5 
```

### Multivariate response model
```{r}
cs_mvmod.t22 <- bf(log.co2pmin_22 | mi() ~ z.log.mass_22 + prior_temp_22 + (1|p|id) + (1|s|series))
cs_mvmod.t24 <- bf(log.co2pmin_24 | mi() ~ z.log.mass_24 + prior_temp_24 + (1|p|id) + (1|s|series)) 
cs_mvmod.t26 <- bf(log.co2pmin_26 | mi() ~ z.log.mass_26 + prior_temp_26 + (1|p|id) + (1|s|series)) 
cs_mvmod.t28 <- bf(log.co2pmin_28 | mi() ~ z.log.mass_28 + prior_temp_28 + (1|p|id) + (1|s|series)) 
cs_mvmod.t30 <- bf(log.co2pmin_30 | mi() ~ z.log.mass_30 + prior_temp_30 + (1|p|id) + (1|s|series)) 
cs_mvmod.t32 <- bf(log.co2pmin_32 | mi() ~ z.log.mass_32 + prior_temp_32 + (1|p|id) + (1|s|series))

brms_mvmod <- brm(formula = cs_mvmod.t22 + cs_mvmod.t24 + cs_mvmod.t26 + cs_mvmod.t28 + cs_mvmod.t30 + cs_mvmod.t32,
                data = wdata, family = gaussian(),
                cores = 3,
                iter = iter,
                warmup = warmup,
                thin = thin)
```
####Mice response impute
### Thermal repeatability of VCO2 at each measurement temperature

```{r}
#Read in model output
cs_mvmod_mi <- readRDS("R/Revision/output/rds/brms_mvmod_mi")

#Diagnostics
plot(cs_mvmod_mi) #One problem plot but not super bad either sd_id_22_intercept
summary(cs_mvmod_mi) #Effective samples not great for intercept variances

y <- posterior_samples(cs_mvmod_mi)
names(posterior_samples(cs_mvmod_mi))

##Hand calculate repeatabilty at each temperature
##22??C
Vbetween <- paste0("sd_id__logco2pmin", 22, "_Intercept")
Vseries <- paste0("sd_series__logco2pmin", 22, "_Intercept") #this is measurement error
Vresidual <- paste0("sigma_logco2pmin", 22)

R <- y[names(y) == Vbetween] /(y[names(y) == Vbetween]  + y[names(y) == Vresidual])
posterior_summary(R)

## Try this again with new function
#Function for calculating repeatability for a character-state brms model
#Repeatability Equation = BtID / (BtID + session + withinID) 
brms_rpt <- function(model.rds.name = cs_mvmod_mi, temp = 22){
  y <- posterior_samples(model.rds.name)
  temp <- temp
  
  Vbetween <- paste0("sd_id__logco2pmin", temp, "_Intercept")
  Vresidual <- paste0("sigma_logco2pmin", temp)
  R <- y[names(y) == Vbetween] /(y[names(y) == Vbetween] + y[names(y) == Vresidual])
  
  rpt_tab <- as.data.frame(matrix(nrow = 1, ncol = 4))
  rownames(rpt_tab) <- paste0("R_t_",temp)
  colnames(rpt_tab) <- colnames(posterior_summary(as.matrix(R)))
  rpt_tab[1,1:4] <- posterior_summary(as.matrix(R))
  return(rpt_tab)
}


#Repeatability at each temperatures
brms_output_rpt <- rbind(brms_rpt(cs_mvmod_mi, temp = 22),
                         brms_rpt(cs_mvmod_mi, temp = 24),
                         brms_rpt(cs_mvmod_mi, temp = 26),
                         brms_rpt(cs_mvmod_mi, temp = 28),
                         brms_rpt(cs_mvmod_mi, temp = 30),
                         brms_rpt(cs_mvmod_mi, temp = 32))

#Repeatability at each temperature
rpt.plot.dat <- as.data.frame(matrix(ncol = 4, nrow = 6))
colnames(rpt.plot.dat) <- c("Temp", "Mean","lower", "upper")
rpt.plot.dat[,1] <- rep(c(seq(22,32, by = 2)))

rpt.plot.dat[,2:4] <- rbind(brms_rpt(cs_mvmod_mi, temp = 22)[c(1,3,4)],
                                 brms_rpt(cs_mvmod_mi, temp = 24)[c(1,3,4)],
                                 brms_rpt(cs_mvmod_mi, temp = 26)[c(1,3,4)],
                                 brms_rpt(cs_mvmod_mi, temp = 28)[c(1,3,4)],
                                 brms_rpt(cs_mvmod_mi, temp = 30)[c(1,3,4)],
                                 brms_rpt(cs_mvmod_mi, temp = 32)[c(1,3,4)])

write.csv(rpt.plot.dat, row.names = F, "R/Revision/output/tabs/Table2_repeatabilty.csv")
```

### Among- and within-individual variance components at each measurement temperature

```{r}
#Compile a dataframe
varcomps <- as.data.frame(matrix(nrow = 12, ncol = 6))
colnames(varcomps) <- c("Type", "Temp", "Mean", "Est.Error", "lower", "upper")
varcomps[,1] <- rep(c("Among Individual","Within Individual"), each= 6)
varcomps[,2] <- rep(seq(22,32, by = 2), 2)

#Among ID variance componenents + CI
varcomps[1:6,3:6] <- posterior_summary(cs_mvmod_mi, "^sd_id")

#Within ID variance components + CI
varcomps[7:12,3:6] <- posterior_summary(cs_mvmod_mi, "^sigma_") 

#Measurement error
posterior_summary(cs_mvmod_mi, "^sigma") 

write.csv(varcomps, row.names = F, "R/Revision/output/tabs/Table2_Among_varcomps.csv")
```

## Variance components

```{r}
#Compile a dataframe
varcomps <- as.data.frame(matrix(nrow = 18, ncol = 6))
colnames(varcomps) <- c("Type", "Temp", "Mean", "Est.Error", "lower", "upper")
varcomps[,1] <- rep(c("Among ID","Measurement Error", "Within ID"), each= 6)
varcomps[,2] <- rep(seq(22,32, by = 2), 3)

#Among ID variance componenents + CI
varcomps[1:6,3:6] <- posterior_summary(cs_mvmod_mi, "^sd_id")

#Measurement error + CI
varcomps[7:12,3:6] <- posterior_summary(cs_mvmod_mi, "^sd_series_") 

#Within ID + CI
varcomps[13:18,3:6] <- posterior_summary(cs_mvmod_mi, "^sigma") 

write.csv(varcomps, row.names = F, "R/Revision/output/tabs/Table2_varcomps_include_ME.csv")
```

### Cross-temperature correlations

```{r}
#Among ID correlations
brms_amongID <- as.data.frame(matrix(nrow = 6, ncol= 6))
colnames(brms_amongID) <-  seq(22,32, by = 2)
rownames(brms_amongID) <-  seq(22,32, by = 2)
diag(brms_amongID) <- rep(1, 6)

#Posterior means
#t22 
brms_amongID[2:6,1] <- brms_amongID[1,2:6] <- posterior_summary(cs_mvmod_mi, "cor_id__logco2pmin22")[,1]

#t24
brms_amongID[3:6,2] <- brms_amongID[2,3:6] <- posterior_summary(cs_mvmod_mi, "cor_id__logco2pmin24")[,1]

#t26
brms_amongID[4:6,3] <- brms_amongID[3,4:6] <- posterior_summary(cs_mvmod_mi, "cor_id__logco2pmin26")[,1]

#t28
brms_amongID[5:6,4] <- brms_amongID[4,5:6] <- posterior_summary(cs_mvmod_mi, "cor_id__logco2pmin28")[,1]

#t30
brms_amongID[6,5] <- brms_amongID[5,6] <- posterior_summary(cs_mvmod_mi, "cor_id__logco2pmin30")[,1]

#Credible intervals for variance and correlations
posterior_summary(cs_mvmod_mi, "^sd_id") 
posterior_summary(cs_mvmod_mi, "cor_id") 

#Within ID correlations
brms_withinID <- as.data.frame(matrix(nrow = 6, ncol= 6))
colnames(brms_withinID) <-  as.factor(seq(22,32, by = 2))
rownames(brms_withinID) <- as.factor(seq(22,32, by = 2))
diag(brms_withinID) <- rep(1, 6)




#Posterior means
#t22
brms_withinID[2:6,1] <- brms_withinID[1,2:6] <- posterior_summary(cs_mvmod_mi, "cor_series__logco2pmin22")[,1]

#t24
brms_withinID[3:6,2] <- brms_withinID[2,3:6] <- posterior_summary(cs_mvmod_mi, "cor_series__logco2pmin24")[,1]

#t26
brms_withinID[4:6,3] <- brms_withinID[3,4:6] <-posterior_summary(cs_mvmod_mi, "cor_series__logco2pmin26")[,1]

#t28
brms_withinID[5:6,4] <- brms_withinID[4,5:6] <-posterior_summary(cs_mvmod_mi, "cor_series__logco2pmin28")[,1]

#t30
brms_withinID[6,5] <- brms_withinID[5,6] <-posterior_summary(cs_mvmod_mi, "cor_series__logco2pmin30")[,1]

#Credible intervals for variance and correlations
Table3c <- posterior_summary(cs_mvmod_mi, "cor_id")[,c(1,3,4)] 
Table3d<- posterior_summary(cs_mvmod_mi, "cor_series")[,c(1,3,4)]

write.csv(Table3c, 'R/Revision/output/tabs/Table3c_amongID.csv')
write.csv(Table3d, 'R/Revision/output/tabs/Table3c_withinID.csv')
```

### Code to generate Figure 2B, Fig 3B, Fig 4 (Bottom panel)

```{r}
#Theme for all ggplots
my_theme <- theme_bw() + 
  theme(legend.position = "none", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=14),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18),
        strip.background = element_rect(fill="white")) 

#Fig 2B Variance components
ggplot(data = varcomps, aes(x = Temp, y = Mean)) +
  geom_point(size = 4) + 
  geom_errorbar(aes(ymax = upper, ymin = lower), width = 0) + 
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  facet_wrap(~Type) + 
  labs(y = expression("Variance"), x = expression(paste("Temperature ",degree,"C"))) + my_theme

#Fig 4 Cross Temperature correlations character state approach
#Among ID correlations
cex.before <- par("cex")
par(cex = 1.2)
corrplot.mixed(as.matrix(brms_amongID), 
               lower.col = "black", upper = "ellipse", 
               tl.col = "black",
               tl.cex = par("cex"))
par(cex = cex.before)


#Within ID correlations
cex.before <- par("cex")
par(cex = 1.2)
corrplot.mixed(as.matrix(brms_withinID), 
               lower.col = "black", upper = "ellipse", 
               tl.col = "black",tl.cex = par("cex"))

par(cex = cex.before)
```

###Fig 2 combined repeatability and variance

```{r}

#Fig 2B Variance components
# ggplot(data = varcomps, aes(x = Temp, y = Mean, group = Type, colour = Type)) +
#   geom_point(aes(shape = Type), size = 6, position = position_dodge(1.6)) + 
#   scale_shape_manual(values= c(6, 2)) + 
#   geom_errorbar(aes(ymin = lower, ymax = upper),width = 0, position = position_dodge(1.6), alpha = 1) +
#   scale_color_manual(values=c("#159FEC", "#159FEC")) + 
#   scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
#   scale_y_continuous(limits = c(0, 0.45), 
#                      breaks = seq(0, 1, by = 0.1),
#                      sec.axis = sec_axis(~.*1, name = "Variance")) +
#   labs(y = expression("Variance"), x = expression(paste("Temperature ",degree,"C"))) + 
#   theme_bw() + 
#   theme(legend.position = "bottom", 
#         legend.text = element_text(size = 12),
#         legend.title = element_text(size = 12),
#         panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(),
#         axis.text=element_text(size=18),
#         axis.title=element_text(size=18),
#         axis.title.y  = element_text(color = "#159FEC", size=18),
#         axis.text.y = element_text(color = "#159FEC", size=18),
#         strip.background = element_rect(fill="white"))

#Fig 2B Variance components
varcomps$Type <- as.factor(varcomps$Type)
varcomps$Type <- factor(varcomps$Type, levels = c("Measurement Error", "Among ID", "Within ID"))

varcomps2 <- transform(varcomps,
          Type = factor(Type, levels = c("Measurement Error", "Among ID", "Within ID")))
                     
top <- ggplot(data = varcomps2, aes(x = Temp, y = Mean)) +
  geom_point(size = 4) + 
  geom_errorbar(aes(ymax = upper, ymin = lower), width = 0) + 
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  facet_wrap(~Type) + 
  labs(y = expression("Variance"), x = expression(paste("Temperature ",degree,"C"))) + my_theme

bottom <- ggplot(data = rpt.plot.dat, aes(x = Temp, y = Mean)) +
  geom_point(shape = 16, colour = "black", size = 6, position = position_dodge(1.6)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper),width = 0, position = position_dodge(1.6), alpha = 1) +
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  scale_y_continuous(limits = c(0, 1), 
                     breaks = seq(0, 1, by = 0.1)) +  
  labs(y = expression("Repeatability"), x = expression(paste("Temperature ",degree,"C"))) +
  theme_bw() + 
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=18),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18),
        strip.background = element_rect(fill="white"))

top + bottom + plot_layout(nrow = 2)


varcomps %<>% select(-Est.Error)
rpt.plot.dat

combined <- rbind(varcomps, rpt.plot.dat)
combined$Type <- as.factor(all_components_plot$Type)
levels(combined$Type) <-c("Among ID", "Within ID", "Repeatabilty", "Measurement Error")

## Combine all three
ggplot(data = combined, aes(x = Temp, y = Mean, group = Type)) +
  geom_point(shape = 16, colour = "black", size = 3, position = position_dodge(1.6)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper),width = 0, position = position_dodge(1.6), alpha = 1) +
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  scale_y_continuous(limits = c(0, 0.6), 
                     breaks = seq(0, 0.6, by = 0.1)) +  
  labs(y = expression("Variance / Repeatabilty"), x = expression(paste("Temperature ",degree,"C"))) +
  facet_grid(~Type) + 
  theme_bw() + 
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=18),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18),
        strip.background = element_rect(fill="white"))

```


### Number of NA

```{r}
## NA in wide data for models
summary(data)

wdata %>% filter(complete.cases(.)) %>% nrow()
ldata %>% filter(complete.cases(.)) %>% nrow()

#For each temp
#22
data %>% filter(is.na(log.co2pmin_22)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 22 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_22)) %>% nrow()
ldata %>% filter(incb_temp == 22 & is.na(log.co2pmin)) %>% nrow()

#24
data %>% filter(is.na(log.co2pmin_24)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 24 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_24)) %>% nrow()
ldata %>% filter(incb_temp == 24 & is.na(log.co2pmin)) %>% nrow()

#26
data %>% filter(is.na(log.co2pmin_26)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 26 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_26)) %>% nrow()
ldata %>% filter(incb_temp == 26 & is.na(log.co2pmin)) %>% nrow()

#28
data %>% filter(is.na(log.co2pmin_28)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 28 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_28)) %>% nrow()
ldata %>% filter(incb_temp == 28 & is.na(log.co2pmin)) %>% nrow()

#30
data %>% filter(is.na(log.co2pmin_30)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 30 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_30)) %>% nrow()
ldata %>% filter(incb_temp == 30 & is.na(log.co2pmin)) %>% nrow()

#32
data %>% filter(is.na(log.co2pmin_32)) %>% pull(series) %>% unique() %>% sort() == ldata %>% filter(incb_temp == 32 & is.na(log.co2pmin)) %>% pull(series) %>% unique() %>% sort()

data %>% filter(is.na(log.co2pmin_32)) %>% nrow()
ldata %>% filter(incb_temp == 32 & is.na(log.co2pmin)) %>% nrow()

#is NA across all 6 temps
data %>% filter(is.na(log.co2pmin_22) | is.na(log.co2pmin_24) | is.na(log.co2pmin_26) | is.na(log.co2pmin_28) | is.na(log.co2pmin_30) | is.na(log.co2pmin_32)) %>% nrow() #This is the problem

data %>% filter(is.na(log.co2pmin_22) | is.na(log.co2pmin_24) | is.na(log.co2pmin_26) | is.na(log.co2pmin_28) | is.na(log.co2pmin_30) | is.na(log.co2pmin_32)) %>% pull(rep_id)  #This is the problem

ldata %>% filter(is.na(log.co2pmin)) %>% nrow()

#Other traits
#is NA in  body mass across all temps
data %>% filter(is.na(z.log.mass_22) | is.na(z.log.mass_24) | is.na(z.log.mass_26) | is.na(z.log.mass_28) | is.na(z.log.mass_30) | is.na(z.log.mass_32)) %>% nrow() #This is the problem

#is NA in prior_temp across all temps
data %>% filter(is.na(prior_temp_22) | is.na(prior_temp_24) | is.na(prior_temp_26) | is.na(prior_temp_28) | is.na(prior_temp_30) | is.na(prior_temp_32)) %>% nrow() #This is the problem

```
```


####Complete case

### Thermal repeatability of VCO2 at each measurement temperature

```{r}
#Read in model output
cs_mvmod <- readRDS("R/Revision/output/rds/brms_mvmod")

#Diagnostics
plot(cs_mvmod) #One problem plot but not super bad either sd_id_22_intercept
summary(cs_mvmod) #Effective samples not great for intercept variances

posterior_samples(cs_mvmod)

#Function for calculating repeatability for a character-state brms model
#Repeatability Equation = BtID / (BtID + session + withinID) 
brms_rpt <- function(model.rds.name = cs_mvmod, temp = 22){
  y <- posterior_samples(model.rds.name)
  temp <- temp
  
  Vbetween <- paste0("sd_id__logco2pmin", temp, "_Intercept")
  Vsession <- paste0("sd_series__logco2pmin", temp, "_Intercept")
  Vresidual <- paste0("sigma_logco2pmin", temp)
  R <- y[names(y) == Vbetween] /(y[names(y) == Vbetween] + y[names(y) == Vsession] + y[names(y) == Vresidual])
  
  rpt_tab <- as.data.frame(matrix(nrow = 1, ncol = 4))
  rownames(rpt_tab) <- paste0("R_t_",temp)
  colnames(rpt_tab) <- colnames(posterior_summary(as.matrix(R)))
  rpt_tab[1,1:4] <- posterior_summary(as.matrix(R))
  return(rpt_tab)
}

#Repeatability at each temperatures
brms_output_rpt <- rbind(brms_rpt(cs_mvmod, temp = 22),
                         brms_rpt(cs_mvmod, temp = 24),
                         brms_rpt(cs_mvmod, temp = 26),
                         brms_rpt(cs_mvmod, temp = 28),
                         brms_rpt(cs_mvmod, temp = 30),
                         brms_rpt(cs_mvmod, temp = 32))

#Repeatability at each temperature
rpt.plot.dat <- as.data.frame(matrix(ncol = 4, nrow = 6))
colnames(rpt.plot.dat) <- c("Temp", "Mean","lower", "upper")
rpt.plot.dat[,1] <- rep(c(seq(22,32, by = 2)))

rpt.plot.dat[,2:4] <- rbind(brms_rpt(cs_mvmod, temp = 22)[c(1,3,4)],
                                 brms_rpt(cs_mvmod, temp = 24)[c(1,3,4)],
                                 brms_rpt(cs_mvmod, temp = 26)[c(1,3,4)],
                                 brms_rpt(cs_mvmod, temp = 28)[c(1,3,4)],
                                 brms_rpt(cs_mvmod, temp = 30)[c(1,3,4)],
                                 brms_rpt(cs_mvmod, temp = 32)[c(1,3,4)])
```

### Among- and within-individual variance components at each measurement temperature

```{r}
#Compile a dataframe
varcomps <- as.data.frame(matrix(nrow = 12, ncol = 6))
colnames(varcomps) <- c("Type", "Temp", "Mean", "Est.Error", "lower", "upper")
varcomps[,1] <- rep(c("Among Individual","Within Individual"), each= 6)
varcomps[,2] <- rep(seq(22,32, by = 2), 2)

#Among ID variance componenents + CI
varcomps[1:6,3:6] <- posterior_summary(cs_mvmod, "^sd_id")

#Within ID variance components + CI
varcomps[7:12,3:6] <- posterior_summary(cs_mvmod, "^sd_series") 

#Measurement error
posterior_summary(cs_mvmod, "^sigma") 

write.csv(varcomps, row.names = F, "R/Revision/output/tabs/Table2.csv")
```

### Cross-temperature correlations

```{r}
#Among ID correlations
brms_amongID <- as.data.frame(matrix(nrow = 6, ncol= 6))
colnames(brms_amongID) <-  seq(22,32, by = 2)
rownames(brms_amongID) <-  seq(22,32, by = 2)
diag(brms_amongID) <- rep(1, 6)

#Posterior means
#t22 
brms_amongID[2:6,1] <- brms_amongID[1,2:6] <- posterior_summary(cs_mvmod, "cor_id__logco2pmin22")[,1]

#t24
brms_amongID[3:6,2] <- brms_amongID[2,3:6] <- posterior_summary(cs_mvmod, "cor_id__logco2pmin24")[,1]

#t26
brms_amongID[4:6,3] <- brms_amongID[3,4:6] <- posterior_summary(cs_mvmod, "cor_id__logco2pmin26")[,1]

#t28
brms_amongID[5:6,4] <- brms_amongID[4,5:6] <- posterior_summary(cs_mvmod, "cor_id__logco2pmin28")[,1]

#t30
brms_amongID[6,5] <- brms_amongID[5,6] <- posterior_summary(cs_mvmod, "cor_id__logco2pmin30")[,1]

#Credible intervals for variance and correlations
posterior_summary(cs_mvmod, "^sd_id") 
posterior_summary(cs_mvmod, "cor_id") 

#Within ID correlations
brms_withinID <- as.data.frame(matrix(nrow = 6, ncol= 6))
colnames(brms_withinID) <-  as.factor(seq(22,32, by = 2))
rownames(brms_withinID) <- as.factor(seq(22,32, by = 2))
diag(brms_withinID) <- rep(1, 6)

#Posterior means
#t22
brms_withinID[2:6,1] <- brms_withinID[1,2:6] <- posterior_summary(cs_mvmod, "cor_series__logco2pmin22")[,1]

#t24
brms_withinID[3:6,2] <- brms_withinID[2,3:6] <- posterior_summary(cs_mvmod, "cor_series__logco2pmin24")[,1]

#t26
brms_withinID[4:6,3] <- brms_withinID[3,4:6] <-posterior_summary(cs_mvmod, "cor_series__logco2pmin26")[,1]

#t28
brms_withinID[5:6,4] <- brms_withinID[4,5:6] <-posterior_summary(cs_mvmod, "cor_series__logco2pmin28")[,1]

#t30
brms_withinID[6,5] <- brms_withinID[5,6] <-posterior_summary(cs_mvmod, "cor_series__logco2pmin30")[,1]

#Credible intervals for variance and correlations
Table3c <- posterior_summary(cs_mvmod, "cor_id")[,c(1,3,4)] 
Table3d<- posterior_summary(cs_mvmod, "cor_series")[,c(1,3,4)]

write.csv(Table3c, 'R/Revision/output/tabs/Table3c_amongID.csv')
write.csv(Table3d, 'R/Revision/output/tabs/Table3c_withinID.csv')
```

### Code to generate Figure 2B, Fig 3B, Fig 4 (Bottom panel)

```{r}
#Theme for all ggplots
my_theme <- theme_bw() + 
  theme(legend.position = "none", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=14),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18),
        strip.background = element_rect(fill="white")) 

#Fig 2B Variance components
ggplot(data = varcomps, aes(x = Temp, y = Mean)) +
  geom_point(size = 4) + 
  geom_errorbar(aes(ymax = upper, ymin = lower), width = 0) + 
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  facet_wrap(~Type) + 
  labs(y = expression("Variance"), x = expression(paste("Temperature ",degree,"C"))) + my_theme

#Fig 4 Cross Temperature correlations character state approach
#Among ID correlations
cex.before <- par("cex")
par(cex = 1.2)
corrplot.mixed(as.matrix(brms_amongID), 
               lower.col = "black", upper = "ellipse", 
               tl.col = "black",
               tl.cex = par("cex"))
par(cex = cex.before)


#Within ID correlations
cex.before <- par("cex")
par(cex = 1.2)
corrplot.mixed(as.matrix(brms_withinID), 
               lower.col = "black", upper = "ellipse", 
               tl.col = "black",tl.cex = par("cex"))

par(cex = cex.before)
```

## Fig 2 combined repeatability and variance

```{r}
rpt.plot.dat$Type <- rep("Repeatability", nrow(rpt.plot.dat))
rpt.plot.dat %<>% arrange(Type, Temp, Mean, lower, upper)

all_components_plot <-rbind(rpt.plot.dat,
                            varcomps %>% dplyr::select(Type, Temp, Mean, lower, upper))

all_components_plot$Type <- as.factor(all_components_plot$Type)
levels(all_components_plot$Type) <-c("Repeatabilty", "Among ID", "Within ID")

#Adding/scaling values so it matches secondary axis
all_components_plot %<>% mutate(Mean = ifelse(Type == "Among ID", Mean*1.5, Mean),
                               lower = ifelse(Type == "Among ID", lower*1.5, lower),
                               upper = ifelse(Type == "Among ID", upper*1.5, upper))


all_components_plot %<>% mutate(Mean = ifelse(Type == "Within ID", (Mean*1.5)+0.18, Mean),
                               lower = ifelse(Type == "Within ID", (lower*1.5)+0.18, lower),
                               upper = ifelse(Type == "Within ID", (upper*1.5)+0.18, upper))


ggplot(data = all_components_plot, aes(x = Temp, y = Mean, group = Type, colour = Type)) +
  geom_point(aes(shape = Type), size = 6, position = position_dodge(1.6)) + 
  scale_shape_manual(values= c(16, 6, 2)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper),width = 0, position = position_dodge(1.6), alpha = 1) +
  scale_color_manual(values=c("#000000","#159FEC", "#159FEC")) + 
  scale_x_continuous(breaks = c(22, 24, 26, 28, 30, 32)) + 
  scale_y_continuous(limits = c(0, 1), 
                     breaks = seq(0, 1, by = 0.1),
                     sec.axis = sec_axis(~.*0.5, name = "Variance")) +
  labs(y = expression("Repeatability"), x = expression(paste("Temperature ",degree,"C"))) +
  theme_bw() + 
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text=element_text(size=18),
        axis.title=element_text(size=18),
        strip.text =element_text(size=18),
        axis.title.y.right = element_text(color = "#159FEC", size=18),
        axis.text.y.right = element_text(color = "#159FEC", size=18),
        strip.background = element_rect(fill="white"))

```

